### 2015-05-12 related.tex
fix

Most related to our work are the static lockset analyzers RELAY~\cite{voung2007relay} and Locksmith~\cite{pratikakis2006locksmith}. Both tools, though, have significant limitations. The authors of RELAY found 5022 warnings when analyzing the Linux kernel, with only 25 of them being true data races. To limit these false positives, RELAY employs post-analysis unsound filters, but these can also filter out true races. Although Locksmith successfully detected data races in several small Pthreads applications and 7 medium-sized Linux device drivers, it also reported a significant number of false positives. The authors also reported that Locksmith was unable to run on several large programs, showcasing its limited scalability. In contrast, \whoop is based on novel over-approximation techniques and uses modern SMT solvers to accelerate state-of-the-art concurrency bug-finders, such as \corral, for precise \emph{and} scalable analysis.

>>>>

Most related to our static lockset analysis are the static lockset analyzers RELAY~\cite{voung2007relay} and Locksmith~\cite{pratikakis2006locksmith}. Both tools, though, have significant limitations. The authors of RELAY found 5022 warnings when analyzing the Linux kernel, with only 25 of them being true data races. To limit these false positives, RELAY employs post-analysis unsound filters, but these can also filter out true races. Although Locksmith successfully detected data races in several small Pthreads applications and 7 medium-sized Linux device drivers, it also reported a significant number of false positives. The authors also reported that Locksmith was unable to run on several large programs, showcasing its limited scalability. In contrast, \whoop is based on novel over-approximation techniques and uses modern SMT solvers to accelerate state-of-the-art concurrency bug-finders, such as \corral, for precise \emph{and} scalable analysis.

Our work is not the first to exploit static analysis for achieving efficient race-checking. Prior work includes: \cite{choi2002efficient}, which combined static analysis, optimized instrumentation and runtime access caching to speedup dynamic data race detection; \cite{kahlon2007fast}, which combined a divide-and-conquer strategy that partitions all pointers of a program that cannot alias in disjoint sets and function summarization to achieve a scalable context-sensitive alias analysis for data races; \cite{kahlon2009semantic}, which used abstract interpretation to achieve a sound partial-order reduction on the set of thread interleavings and statically reduce the number of false data race warnings; and \cite{das2015section}, which combined inter-procedural pointer analysis with verifiable user annotations to split programs into disjoint sections, based on non-communicating accesses of shared data, and eliminate redundant checks during dynamic race detection.
